### 2019-07-02 sections/language.tex
Fixed reviewer comments. One TODO left; fix proofs

Editors that hold an expression $e : \tau$ have type $\Task \tau$.
Empty editors are annotated with a type in order to ensure type safety.
Without type annotations, it would be possible to change the type of an editor, by clearing it and filling it with a value of different type.

>>>>

Editors that hold an expression $e : \tau$ have type $\Task \tau$.
Empty editors are annotated with a type in order to ensure type safety and type preservation during evaluation.

### 2019-07-02 sections/properties.tex
Todo's from reviews
Fixed reviewer comments. One TODO left; fix proofs

\begin{theorem}[Type preservation under evaluation]
  % For all well typed expressions $e$ and states $\sigma$,
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\tau$ and $\Gamma,\Sigma \infers \sigma$,
  if $e,\sigma \evaluate e',\sigma'$,
  then $\Gamma,\Sigma \infers e':\tau$ and $\Sigma \infers \sigma'$.
  \label{thm:pres-eval}
\end{theorem}

\noindent
Where $\Sigma \infers \sigma$ means that for all $l\in \sigma$, it holds that
$\Sigma(l)=\Gamma,\Sigma\infers \sigma(l)$.

\begin{theorem}[Type preservation under normalisation]
  % For all well typed expressions $e$ and states $\sigma$,
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Sigma \infers \sigma$,
  if $e,\sigma \normalise e',\sigma'$,
  then $\Gamma,\Sigma \infers e':\Task\tau$ and $\Sigma \infers \sigma'$.
  \label{thm:pres-norm}
\end{theorem}

\begin{theorem}[Type preservation under handling]
  % For all well typed expressions $e$, states $\sigma$, and inputs $i$,
  For all expressions $e$, states $\sigma$ and inputs $i$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Sigma \infers \sigma$,
  if $ e,\sigma \handle{i} e',\sigma'$,
  then $\Gamma,\Sigma\infers e':\Task\tau$ and $\Sigma\infers \sigma'$.
  \label{thm:pres-handle}
\end{theorem}

>>>>

\begin{theorem}[Type preservation under evaluation]
  % For all well typed expressions $e$ and states $\sigma$,
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\tau$ and $\Gamma,\Sigma \infers \sigma$,
  if $e,\sigma \evaluate e',\sigma'$,
  then $\Gamma,\Sigma \infers e':\tau$ and $\Gamma,\Sigma \infers \sigma'$.
  \label{thm:pres-eval}
\end{theorem}

\noindent
Where $\Gamma,\Sigma \infers \sigma$ means that for all $l\in \sigma$, it holds that
$\Gamma,\Sigma\infers \sigma(l):\Sigma(l)$.

\begin{theorem}[Type preservation under normalisation]
  % For all well typed expressions $e$ and states $\sigma$,
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Gamma,\Sigma \infers \sigma$,
  if $e,\sigma \normalise e',\sigma'$,
  then $\Gamma,\Sigma \infers e':\Task\tau$ and $\Gamma,\Sigma \infers \sigma'$.
  \label{thm:pres-norm}
\end{theorem}

\begin{theorem}[Type preservation under handling]
  % For all well typed expressions $e$, states $\sigma$, and inputs $i$,
  For all expressions $e$, states $\sigma$ and inputs $i$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Gamma,\Sigma \infers \sigma$,
  if $ e,\sigma \handle{i} e',\sigma'$,
  then $\Gamma,\Sigma\infers e':\Task\tau$ and $\Gamma,\Sigma\infers \sigma'$.
  \label{thm:pres-handle}
\end{theorem}
